Ear canal dynamic motion piezoelectric energy harvester using a bistable resonator cycled by coupled hydraulic switches made of collapsed flexible tubes.

### 2022-10-11 article_system.tex
update

We can estimate the best choice maximizing the energy extraction from the hydraulic source. Figure \ref{fig:OB_vs_LINEAR} shows in blue the hydraulic behavior of the ideal flow rate source previously introduced with the upper limit values of pressure and volume variations. To be harvested, the energy has to be stored in a mechanical potential reservoir at first, to be then converted in electricity by the transducer. The hydraulic-mechanic interface can be a hydraulic cylinder. In this way, the best linear resonator can theoretically exploit/store a maximum of $50\%$ from the maximum available hydraulic energy ($\text{max}(E_{hyd})$). Furthermore, BR usually admit non-linear elastic behavior. For example, a BR governed by a Duffing equation is inherently capable of exploiting $65$\% from the same energy source, which is $15$\% better than the best theoretical linear option.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={22.5cm 0cm 0cm 8.8cm},clip, width=0.35\textwidth]{figures/OB_vs_LINEAR.pdf}
	\caption{Hydraulic source exploitation depending on the mechanical load}
	\label{fig:OB_vs_LINEAR}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Hence, the absence of rubbing parts and the optimal energy extraction shed light on a BR as a promising solution for our application. 
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
\section{HARVESTER PRESENTATION AND OPERATION \mbox{PRINCIPLE}}
\label{sec:HARVESTER PRESENTATION AND OPERATION PRINCIPLE}
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%

>>>>

We can estimate the best choice maximizing the energy extraction from the hydraulic source. Figure \ref{fig:OB_vs_LINEAR} shows in blue the hydraulic behavior of the ideal flow rate source previously introduced with the upper limit values of pressure and volume variations. To be harvested, the energy has to be stored in a mechanical potential reservoir at first, to be then converted in electricity by the transducer. The hydraulic-mechanic interface can be a hydraulic cylinder (HC). It could store then the energy in the frequency-up converter by actuating it at the frequency of human mastication. Figure \ref{fig:hydraulic_mechanic_interface} schematizes the mechanical interaction between the HC and the resonator assimilated to a spring of stiffness $K_s$.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={19.7cm 0cm 0cm 13cm},clip, width=0.6\linewidth]{figures/hydraulic_mechanic_interface.pdf}
	\caption{Hydraulic source exploitation depending on the mechanical load}
	\label{fig:hydraulic_mechanic_interface}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The potential energy then stored in a linear resonator can be expressed as follows :
\begin{equation}
	Ep_{lin} = \dfrac{K_{lin}\ x_{hc}^2}{2}
\end{equation}
Where $K_{lin}$ models the linear resonator stiffness and $x_{hc}$ the HC piston stroke. During the actuation, the forces applied on each side of the HC are equal, which models the hydraulic-mechanic interface (eq. \ref{eq:hydraulic-mechanic_interface}).
\begin{equation}
	\Delta p_{ear}\ S_{hc} = K_{lin}\ x_{hc}
	\label{eq:hydraulic-mechanic_interface}
\end{equation}
theoretically exploit/store a maximum of $50\%$ from the maximum available hydraulic energy ($\text{max}(E_{hyd})$). Yest, BRs usually admit non-linear elastic behavior. For example, a BR governed by a Duffing equation is inherently capable of exploiting $65$\% from the same energy source, which is $15$\% better than the best theoretical linear option.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={22.5cm 0cm 0cm 8.8cm},clip, width=0.35\textwidth]{figures/OB_vs_LINEAR.pdf}
	\caption{Hydraulic source exploitation depending on the mechanical load}
	\label{fig:OB_vs_LINEAR}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Hence, the absence of rubbing parts and the optimal energy extraction shed light on a BR as a promising solution for our application. 
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
\section{HARVESTER PRESENTATION AND OPERATION \mbox{PRINCIPLE}}
\label{sec:HARVESTER PRESENTATION AND OPERATION PRINCIPLE}
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
